Abstractions for Type-Level Programming

### 2022-04-22 article.tex
Address Dragana's comments
Do TODO

>>>>

\subsection{Comparison to Generalized Singleton Types}

In \Cref{chap:generalizing-singleton-types}, we presented a generalization of singleton types for type-level programing.
Generalized singletons and match types share some similarities, such as the notion of disjointness which plays an important role in both features.
The two features relate on deeper level: we can explain match types in terms of generalized singletons.
For example, the we can give an alternative definition of |Elem| match type using a generalized singleton:
%
\begin{lstlisting}
type Elem[X] = { (_: X) match
  case _: String => (_: Char)
  case _: List[t] => (_: Elem[t])
  case _: Any => (_: X)
}
\end{lstlisting}
%
This definition makes the term/type correspondence evident: the |Elem[X]| type reduces in the way than the corresponding match expression.
